Distortion-corrected kernel density estimate on Riemannian manifolds

### 2022-10-10 paper/paper.Rmd
Update all twin peaks plots in Rmd, need to be knited

```{r tpisomapden, fig.align = 'center', out.width = "95%", fig.cap="Scatterplot of true density and estimated density ranks of ISOMAP embedding for DC-KDE and KDE, with colors indicating the absolute rank errors weighted by the sum of true and estimated ranks. DC-KDE shows a strong linear positive relationship with a higher rank correlation compared to KDE.", echo = FALSE}
# knitr::include_graphics("figures/Twin Peak2000_density_isomap_r0_5_rank_nocolor.png")
knitr::include_graphics("figures/Twin Peak2000_densityrank_comparison_isomap_radius8_r0_5_logrank_rec_colprob_circlefalse.png")
knitr::include_graphics("figures/Twin Peak2000_densityrank_comparison_isomap_radius8_r0_5_logrank_rec_nocolprob_circlefalse.png")
```

>>>>

```{r tpisomapden, fig.align = 'center', out.width = "100%", fig.cap="Scatterplot of true density and estimated density ranks of ISOMAP embedding for DC-KDE and KDE, with colors indicating the absolute rank errors weighted by the sum of true and estimated ranks. DC-KDE shows a strong linear positive relationship with a higher rank correlation compared to KDE.", echo = FALSE}
# knitr::include_graphics("figures/Twin Peak2000_density_isomap_r0_5_rank_nocolor.png")
knitr::include_graphics("figures/Twin Peak2000_densityrank_comparison_isomap_radius8_r0_5_logrank_rec_colprob_crossfalse.png")
```

```{r tptsneden, fig.align = 'center', out.width = "100%", fig.cap="Scatterplot of true density and estimated density ranks of t-SNE embedding for DC-KDE and KDE, with colors indicating the absolute rank errors weighted by the sum of true and estimated ranks. DC-KDE shows a strong linear positive relationship with a higher rank correlation compared to KDE.", echo = FALSE}
knitr::include_graphics("figures/Twin Peak2000_densityrank_comparison_tsne_radius8_r0_5_logrank_rec_colprob_crossfalse.png")
```
